Collapsed Cores in Globular Clusters, \\ Gauge-Boson Couplings, and AAS\TeX\ Examples

### 2014-03-14 tex/paper1/paper1.tex
added in images
edits to the paper; starting with considering random pixesl, then motivating geometric means and models

We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.

@@

The arithmetic and geometric mean power spectra were formed from all
the time-series in each region.  A third power spectrum was created by
first summing all the data in a region, applying the
normalization/apodization procedure described above, and then
calculating the Fourier power spectrum.  These three power spectra
then summarize the Fourier power in each region, for each wavebad
studied.  Figures \ref{fig:arith171} and \ref{fig:geom171} shows the
arithmetic and geometric mean power spectra for each region in AIA
171\AA.  Figures \ref{fig:arith193} and \ref{fig:geom193} show the
arithmetic and geometric mean power spectra for each region in AIA
193\AA.  Each mean power spectrum is also fit with a power spectrum of
the form
\begin{equation}
\label{eq:pwrlaw}
P(f) = Af^{-n} + C
\end{equation}
where $f$ is the frequency, $n$ is the power law index, $A$ a
normalization constant and $C$ is a background power.  Note that in
these plots, a least-squares fitting algorithm is used to fit this
model to the data.  The fit here is intended to show the approximate
power-law nature of the observed Fourier power spectrum.

\begin{figure}
\label{fig:arith171}

@@

@@

\begin{figure}
\label{fig:arith193}

@@

\subsection{Initial inspection of the power spectra}\label{ssec:init}

>>>>

We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figures \ref{fig:loc171} and \ref{fig:loc193} show the location of the
regions on sample images from the time range considered.

\begin{figure}
\label{fig:loc171}

\begin{figure}
\label{fig:loc193}

@@

Figures \ref{fig:demo171} and \ref{fig:demo193} show example power
spectra, plotted using a log-log scale from individual pixels inside
each of the regions shown in Figures \ref{fig:loc171} and
\ref{fig:loc193}.  The shape of the power spectra indicate that the
Fourier power follows a power law approximately.

\begin{figure}
\label{fig:demo171}

\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (Figure \protect\ref{fig:loc171}).  The vertical black lines
  indicate the 3 and 5 minute frequencies. The equivalent plot in the
  AIA 193\AA\ waveband is shown in Figure \protect\ref{fig:demo193}.}
\end{figure}

\begin{figure}
\label{fig:demo193}

\caption{Log-log plot of the Fourier power of a time-series at the AIA
  pixel overlying a randomly chosen pixel in each of the regions
  considered (Figure \protect\ref{fig:loc193}).  The vertical black lines
  indicate the 3 and 5 minute frequencies. The equivalent plot in the
  AIA 171\AA\ waveband is shown in Figure \protect\ref{fig:demo171}.}
\end{figure}

Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
of the logarithm of the Fourier power for certain frequencies in the
spectrum.  The distributions all approximately follow a normal
distribution.  This indicates that the power in each each at each
frequency is approximately log-normally distributed.  This observation
guides the choice of how to average the power spectrum over each of
the selected physical regions.  Since the Fourier power is
log-normally distributed, the arithmetic mean of the Fourier power is
biased by the very largest powers.  Hence the mean of the logarithm of
the Fourier power is considered, which is equivalent to the geometric
mean of the Fourier power.

\begin{figure}
\label{fig:dist171}

@@

\begin{figure}
\label{fig:dist193}

These geometric mean Fourier power spectra are shown in Figures
\ref{fig:geom171} and \ref{fig:geom193}, for each of the physical
regions considered.  It is clear that the Fourier power spectra
exhibit power-law like characteristics.

@@

@@

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eq:pwrlaw}
P_{0}(f) = Af^{-n} + C,
\end{equation}
where $A>0$ is a proportionality constant, $n>0$ is the power law
index, and $C>0$ describes the high-frequency Fourier power.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of uncorrelated and incoherent Fourier power.  This suggests that a
second model for these regions should be considered.  The spectrum
$P_{1}$ where
\begin{equation}
\label{eq:pwrlawbunp}
\ln P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}
\end{equation}
contains the previous power law dependence, plus the second term,
modelling the excess power.
